Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-14 Supplemental-Material-B-Annotated-Analysis.Rmd
worker qual keyneed random intercept added

@@

@@

>>>>

#### random slope

@@

\begin{equation}
(\#eq:WorkerOutQualEmptyModel)
Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
\end{equation}

```{r workerNullQualKeyNeed}
# Create and save Model
  Null.Out.Qual.ML.r = lme4::lmer(quality_overall_1~1 + (1|PID),data=workerOutgroupInteraction) #use optim if it does not converge
  Null.Out.Qual.ML = lme(quality_overall_1~1,random=~1|PID, data=workerOutgroupInteraction, control=list(opt="nlmimb")) #use optim if it does not converge

# Get summary with p-values (Satterthwaite's method)
  #summary(Null.ML.r) #or with the lme function
  summ(Null.Out.Qual.ML.r, digits = 3, center = TRUE)

# Save variances
  v.out.qual.null <- VarCorr(Null.Out.Qual.ML) # save variances
# The estimate of (between-group or Intercept variance, tau_{00}^2):
  tau <- as.numeric(v.out.qual.null[1])
# and the estimate of (within-group or residual variancel, sigma^2) is:
  sigma <- as.numeric(v.out.qual.null[2])
# The ICC estimate (between/between+within) is:
  ICC <- (as.numeric(v.out.qual.null[1])/(as.numeric(v.out.qual.null[1])+as.numeric(v.out.qual.null[2])))
  ICC.Perc <- ((as.numeric(v.out.qual.null[1])/(as.numeric(v.out.qual.null[1])+as.numeric(v.out.qual.null[2]))))*100
```

@@

```{r workerInterceptQualKeyNeed}
# Create and save Model
  model.qual.keyneed = lme(quality_overall_1 ~ keymotive_fulfillemt_1, random=~1|PID,data=workerOutgroupInteraction)

# Get summary with p-values (Satterthwaite's method)
  summ(lmer(quality_overall_1 ~ keymotive_fulfillemt_1 + (1|PID),data=workerOutgroupInteraction), 
       confint = TRUE, digits = 3, center = TRUE)

# Compare new model to previous step
  anova(Null.Out.Qual.ML, model.qual.keyneed) %>%
    as.data.frame %>%
    select(-call) %>%
    kbl(., 
        #label = "",
        caption = "Worker: Model Comparison",
        format = "html", 
        linesep = "",
        booktabs = T,
        align = rep('c', ncol(.)),
        digits = 3)  %>%
  kable_styling(position = "left")

# Save variances
  v.qual.keyneed <- lme4::VarCorr(model.qual.keyneed)

# The estimate of between-group (or Intercept variance) explained: 
  # Variance Explained = 1 – (Var with Predictor/Var without Predictor)
    v.qual.keyneed.btw <- 1 - (as.numeric(v.qual.keyneed[1])/as.numeric(v.out.qual.null[1]))
    v.qual.keyneed.btw.perc <-  (1 - (as.numeric(v.qual.keyneed[1])/as.numeric(v.out.qual.null[1])))*100
  # and the estimate of within-group (or residual variancel) explained is:
    v.qual.keyneed.within <- 1 - (as.numeric(v.qual.keyneed[2])/as.numeric(v.out.qual.null[2]))
    v.qual.keyneed.within.perc <- (1 - (as.numeric(v.qual.keyneed[2])/as.numeric(v.out.qual.null[2])))*100
```

#### random slope
